---
title: "Homework 8"
author: "Xinqian Dai"
date: "10/31/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
chooseCRANmirror(graphics=FALSE, ind=1)
library(formatR)
knitr::opts_chunk$set(tidy.opts = list(width.cutoff = 60), tidy = TRUE)
```


```{r set up workspace}
library(ggplot2)
library(tidyverse)
library(moderndive)
library(skimr)
library(infer)
library(dbplyr)
setwd("~/Desktop")
load(file="covid_example_population.RData")
load(file="US_COVID19_21_10_26.RData")
```

##1

###a
```{r}
sample1 <- covid_pop %>% sample_n(1000)
sample1 %>% summarize(infectedprop=sum(infected=="infected")/1000) 
```
###b
```{r}
bootstrap_distribution <- sample1 %>% specify(response = infected, success = "infected") %>% generate(reps = 1000, type = "bootstrap") %>% calculate(stat = "prop")

percentile_ci <- bootstrap_distribution %>% get_confidence_interval(level = 0.90, type = "percentile")
percentile_ci
visualize(bootstrap_distribution) + shade_confidence_interval(endpoints = percentile_ci )+labs(x = "Stat", y = "Count", title = "size 1000 90% percentile bootstrap")

```
90% CI: (0.027, 0.046)

### c
```{r}
standard_error_ci <- bootstrap_distribution %>% get_confidence_interval(level = 0.9, type = "se", point_estimate = 0.032)

standard_error_ci

visualize(bootstrap_distribution) + shade_confidence_interval(endpoints = standard_error_ci)+labs(x = "Stat", y = "Count", title = "se bootstrap")

```
90% CI: (0.0224, 0.0416)

###d
```{r}
percentile_ci <- bootstrap_distribution %>% get_confidence_interval(level = 0.99, type = "percentile")
percentile_ci
visualize(bootstrap_distribution) + shade_confidence_interval(endpoints = percentile_ci )+labs(x = "Stat", y = "Count", title = "size 1000 99% percentile bootstrap")


percentile_ci <- bootstrap_distribution %>% get_confidence_interval(level = 0.80, type = "percentile")
percentile_ci
visualize(bootstrap_distribution) + shade_confidence_interval(endpoints = percentile_ci )+labs(x = "Stat", y = "Count", title = "size 1000 80% percentile bootstrap")

```
99% percentile bootstrap confidence interval is the widest and 80% percentile bootstrap confidence interval is the narrowest. That's because higher confidence levels tend to produce wider confidence intervals. 99% CI means that we are 99% confident that the true mean is in the interval while 80% CI means we are 80% confident that the true mean is fall into the interval, so it is narrower than 99%CI.

###e
```{r}
bootstrap_distribution2 <- sample1 %>% specify(response = infected, success = "infected") %>% generate(reps = 1000, type = "bootstrap") %>% calculate(stat = "prop")

percentile_ci <- bootstrap_distribution2 %>% get_confidence_interval(level = 0.90, type = "percentile")
percentile_ci
visualize(bootstrap_distribution2) + shade_confidence_interval(endpoints = percentile_ci )+labs(x = "Stat", y = "Count", title = "size 1000 90% percentile bootstrap")

bootstrap_distribution3 <- sample1 %>% specify(response = infected, success = "infected") %>% generate(reps = 1000, type = "bootstrap") %>% calculate(stat = "prop")

percentile_ci <- bootstrap_distribution3 %>% get_confidence_interval(level = 0.90, type = "percentile")
percentile_ci
visualize(bootstrap_distribution3) + shade_confidence_interval(endpoints = percentile_ci )+labs(x = "Stat", y = "Count", title = "size 1000 90% percentile bootstrap")


bootstrap_distribution4 <- sample1 %>% specify(response = infected, success = "infected") %>% generate(reps = 1000, type = "bootstrap") %>% calculate(stat = "prop")

percentile_ci <- bootstrap_distribution4 %>% get_confidence_interval(level = 0.90, type = "percentile")
percentile_ci
visualize(bootstrap_distribution4) + shade_confidence_interval(endpoints = percentile_ci )+labs(x = "Stat", y = "Count", title = "size 1000 90% percentile bootstrap")

```
The intervals and lengths are not the same but not much different from each other. That is because the re-samples from the same original sample cannot be promised to be exactly the same as each other.

###f
```{r}
sample2 <- covid_pop %>% sample_n(1000)
bootstrap_distribution5 <- sample2 %>% specify(response = infected, success = "infected") %>% generate(reps = 1000, type = "bootstrap") %>% calculate(stat = "prop")

percentile_ci <- bootstrap_distribution5 %>% get_confidence_interval(level = 0.90, type = "percentile")
percentile_ci
visualize(bootstrap_distribution5) + shade_confidence_interval(endpoints = percentile_ci ) + labs(x = "Stat", y = "Count", title = "size 1000 90% percentile bootstrap")


sample3 <- covid_pop %>% sample_n(1000)
bootstrap_distribution6 <- sample3 %>% specify(response = infected, success = "infected") %>% generate(reps = 1000, type = "bootstrap") %>% calculate(stat = "prop")

percentile_ci <- bootstrap_distribution6 %>% get_confidence_interval(level = 0.90, type = "percentile")
percentile_ci
visualize(bootstrap_distribution6) + shade_confidence_interval(endpoints = percentile_ci )+ labs(x = "Stat", y = "Count", title = "size 1000 90% percentile bootstrap")


sample4 <- covid_pop %>% sample_n(1000)
bootstrap_distribution7 <- sample4 %>% specify(response = infected, success = "infected") %>% generate(reps = 1000, type = "bootstrap") %>% calculate(stat = "prop")

percentile_ci <- bootstrap_distribution7 %>% get_confidence_interval(level = 0.90, type = "percentile")
percentile_ci
visualize(bootstrap_distribution7) + shade_confidence_interval(endpoints = percentile_ci ) + labs(x = "Stat", y = "Count", title = "size 1000 90% percentile bootstrap")


```
The intervals and lengths are not the same and they are more different from each other from the previous part because these re-samples don't even have the same original sample.


###g
```{r}
sample5 <- covid_pop %>% sample_n(2000)
bootstrap_distribution8 <- sample5 %>% specify(response = infected, success = "infected") %>% generate(reps = 2000, type = "bootstrap") %>% calculate(stat = "prop")

percentile_ci <- bootstrap_distribution8 %>% get_confidence_interval(level = 0.90, type = "percentile")
percentile_ci
visualize(bootstrap_distribution8) + shade_confidence_interval(endpoints = percentile_ci )+ labs(x = "Stat", y = "Count", title = "size 2000 90% percentile bootstrap")
```
This confidence interval is narrower than that in part b.

###h
```{r}
covid_pop %>% summarize(infectedprop=sum(infected=="infected")/10000) 
```
All my intervals above captured the truth as I expected, but since we use random samplings, we cannot guarantee that our graphs will always capture the truth.


##2

Each of the confidence intervals either does or doesn’t contain the true parameter so the probability is either a 1 or a 0, the confidence interval only represents our confidence in capturing the truth.


##3

###a
```{r}
us_counties <- us_counties %>% mutate(cases_per_100000 = cases / pop_2019 * 100000)
us_counties %>% group_by(region) %>% summarise(mean = mean(cases_per_100000), sd = sd(cases_per_100000))
```
###b
```{r}
neandwregion <- us_counties %>% filter(region %in% c("Northeast","West"))
bootstrap <- neandwregion %>% specify(formula = cases_per_100000 ~ region) %>% generate(reps = 1000, type = "bootstrap") %>% calculate(stat = "diff in means",order = c("Northeast", "West"))
percentile_ci_new <- bootstrap %>% get_confidence_interval(level = 0.90, type = "percentile")
percentile_ci_new
visualize(bootstrap) + shade_confidence_interval(endpoints = percentile_ci_new)+ labs(x = "Cases per 100000", y = "Count", title = "Bootstrap for the difference in mean county cases per 100000")
```
0 is not part of my interval and it is not plausible that the mean county COVID rates are not different between the northeast and west.


###c
```{r}
us_counties %>% group_by(region) %>% summarise(averages_over_people = sum(cases) / sum(pop_2019) * 100000)
```
Why do you think they are larger/smaller?

The rate of COVID cases per 100000 people in Northeast is higher than the county-wide averages while the rate in other 3 regions is lower than the county-wide averages. Maybe that's because the size of counties in Northeast is relatively small and it leads to a small county-wide average.

