---
title: "Homework 5"
author: "Xinqian Dai"
date: "10/10/2021"
output:
  word_document: default
  pdf_document: default
---
```{r setup, include=FALSE}
library(formatR)
knitr::opts_chunk$set(tidy.opts = list(width.cutoff = 60), tidy = TRUE)
knitr::opts_chunk$set(echo = TRUE)
chooseCRANmirror(graphics=FALSE, ind=1)
```

```{r set up workspace}
library(ggplot2)
library(dplyr)
library(gridExtra)
library(zoo)
library(tinytex)
library(lubridate)
library(tidyverse)
library(moderndive)
library(skimr)
setwd("/Users/demix9/Desktop")
load(file="MA_COVID19_21_09_28.RData")
load(file="MA_county_variables_2020.RData")
```


```{r make_variables}
load(file="MA_COVID19_21_10_05.RData")
load(file="MA_county_variables_2020.RData")

ma_extra <- ma_extra %>% mutate(pct_over_85=100*X2019_age_85_plus/X2019_pop_est)
ma_extra <- ma_extra %>% mutate(pct_white=100*pct_NHWA_2019)
ma_extra <- ma_extra %>% mutate(pct_nonwhite=100-pct_white)

mass_total_deaths_cases <- mass %>% filter(date==max(date)) %>% select(county, deaths, cases)

ma_extra <- ma_extra %>% inner_join(mass_total_deaths_cases, by="county")

ma_extra <- ma_extra %>% mutate(cases_per_capita=cases/X2019_pop_est,
 deaths_per_capita=deaths/X2019_pop_est)

ma_extra <- ma_extra %>% mutate(deaths_per_100000 = 100000*deaths_per_capita)
ma_extra <- ma_extra %>% mutate(cases_per_100000 = 100000*cases_per_capita)

ma_extra <- ma_extra %>% mutate(region=case_when(
 county %in% c("Hampshire", "Franklin", "Hampden","Berkshire", "Worcester") ~ "West",
 #county %in% c("Worcester") ~ "Central",
 county %in% c("Essex", "Middlesex", "Suffolk","Norfolk") ~ "East",
 county %in% c("Bristol", "Plymouth", "Barnstable", "Dukes", "Nantucket") ~ "Cape"
) )

```
## 1

### a

```{r}
glimpse(ma_extra)
ma_extra %>% sample_n(size = 1)
toSkim <- ma_extra %>% select(people_per_Housing, region, deaths_per_100000)
skim_without_charts(toSkim)
table(ma_extra$region)
ma_extra %>% ggplot(aes(x = people_per_Housing, y = deaths_per_100000)) + geom_point()+ ggtitle("Deaths per 100000 vs People per housing")+labs(x = "People per housing", y = "Deaths per 100000") + geom_smooth(method = "lm", se = FALSE) 
ma_extra %>% ggplot(aes(x = people_per_Housing, y = deaths_per_100000, color = region)) + geom_point()+ ggtitle("Deaths per 100000 vs People per housing")+labs(x = "People per housing", y = "Deaths per 100000", color = "Region")+ geom_smooth(method = "lm", se = FALSE) 
ma_extra %>% ggplot(aes(x = region, y = people_per_Housing)) + geom_point()+ ggtitle("People per housing by Region")+labs(x = "Region", y = "People per housing", color = "Region")+ geom_smooth(method = "lm", se = FALSE) 
```
According to the second graph, the two predictor variables are not related to each other.

### b

```{r}
interaction_model <- lm(deaths_per_100000 ~ region * people_per_Housing, data = ma_extra)
get_regression_table(interaction_model)

```

$\hat{y}=b_0 + b_1*PPH + b_2 *(East or not) + b_3 (West or not) + b_4 (PPH* East or not) + b_5 (PPH* West or not) = -119.549 + 180.665* PPH - 149.306(East or not) + 219.303 (West or not) + 35.384(PPH * East or not) -113.661(PPH * West or not)$
The coefficient of Cape is 0.011,
The coefficient of East is 0.011+0.031 = 0.042,
The coefficient of West is 0.011+0.008 = 0.019.

### c
For Cape :
$\hat{y}= -119.549 + 180.665* PPH $ 
For East :
$\hat{y}= -119.549 + 180.665* PPH - 149.306 + 35.384* PPH = -268.855 + 216.049* PPH$  
For West :
$\hat{y}= -119.549 + 180.665* PPH + 219.303 - 113.661* PPH = 99.754 + 67.004* PPH$

### d
```{r}
ma_extra %>% ggplot(aes(x = people_per_Housing, y = deaths_per_100000, color = region)) + geom_point()+ ggtitle("People per housing by Region")+labs(x = "Region", y = "People per housing", color = "Region")+ geom_parallel_slopes(se = FALSE) 
```
Yes. They seem much different because the three lines in the first graph have very different slopes.

### e
```{r}
parallel_model <- lm(deaths_per_100000 ~ region + people_per_Housing, data = ma_extra)
get_regression_table(parallel_model)
```

$\hat{y}=b_0 + b_1*PPH + b_2 (East or not) + b_3 (West or not) = -96.150 +166.079* PPH -49.775(East or not) -26.390 (West or not)$

### f
$Cape:\hat{y}= -96.150+ 166.079 * PPH$
$East:\hat{y}=-96.150 + 166.079 * PPH -49.775 = 145.925 + 166.079 * PPH$
$West:\hat{y}=-96.150 + 166.079 * PPH -26.390 = 122.540 + 166.079 * PPH$

There’s no people_per_Housing:regionEast and people_per_Housing:regionWest in this fit and the coefficients for the three regions are the same.

### g
```{r}
ppt_only <- lm(deaths_per_100000 ~ people_per_Housing, data = ma_extra)
region_only <- lm(deaths_per_100000 ~ region, data = ma_extra)
sse_ppt_only <- get_regression_points(ppt_only) %>% select(residual) %>% mutate(squared_error = residual ^2) %>% summarize(sum(squared_error))
sse_region_only <- get_regression_points(region_only) %>% select(residual) %>% mutate(squared_error = residual ^2) %>% summarize(sum(squared_error))
sse_interaction_model <- get_regression_points(interaction_model) %>% select(residual) %>% mutate(squared_error = residual ^2) %>% summarize(sum(squared_error))
sse_parallel_model <- get_regression_points(parallel_model) %>% select(residual) %>% mutate(squared_error = residual ^2) %>% summarize(sum(squared_error))
sses <- c(sse_ppt_only,sse_region_only, sse_interaction_model, sse_parallel_model )
sse_names <- c("PPT only" , "Region only", "Interaction model", "Paralle Slopes model")
names(sses) <- sse_names
knitr::kable(as.matrix(sses), row.names = T)
```
### h
Region only explains more variation; 
Yes, adding the second variable substantially improves the model fit because the SSE is smaller after adding the variable;
No, the interaction model doesn't substantially improve the model fit beyond the parallel slopes model fit because its SSE is just slightly smaller than that of the parallel sloped model;
I prefer parallel sloped model because its SSE is almost the same as the interaction model but it's much more simple.



## 2

### a
Simpson's paradox is a phenomenon in which a trend appears in several groups of data but disappears or reverses when the groups are combined. 

### b

We could see below that Deaths_per_100000 for east region is the most and Deaths_per_100000 for West is the second greatest but this is not always true with different PPHs so there's a paradox.

```{r}
ma_extra %>% group_by(region) %>%ggplot(aes(x = region, y = deaths_per_100000)) + geom_boxplot()+ ggtitle("Deaths per 100000 by Region")+labs(x = "Region", y = "Deaths per 100000")

ma_extra %>% ggplot(aes(x = region, y = deaths_per_100000, color = people_per_Housing)) + geom_point()+ ggtitle("Deaths per 100000 by Region")+labs(x = "Region", y = "Deaths per 100000", color = "PPH")+ geom_parallel_slopes(se = FALSE) 
```

### c
Suppose we’re in the soft drinks industry and we’re trying to choose between two new flavors we’ve produced. We could sample public opinion on the two flavors — let’s say we choose to do so by setting up two sampling stalls for each flavor in a busy area and asking 1000 people at each stall if they enjoy the new flavor.

We can see that 80% of people enjoyed ‘Sinful Strawberry’ whereas only 75% of people enjoyed ‘Passionate Peach’. So ‘Sinful Strawberry’ is more likely to be the preferred flavor.
Now, suppose our marketing team collected some other information while conducting the survey, such as the sex of the person sampling the drink. 

This suggests that 84.4% of men and 40% of women liked ‘Sinful Strawberry’ whereas 85.7% of men and 50% of women liked ‘Passionate Peach’. According to our sample data, generally people prefer ‘Sinful Strawberry’, but both men and women separately prefer ‘Passionate Peach’. 

Resource: https://towardsdatascience.com/simpsons-paradox-and-interpreting-data-6a0443516765#:~:text=One%20of%20the%20most%20famous,35%25%20of%20their%20female%20applicants.

