---
title: "Homework 7"
author: "Xinqian Dai"
date:  "10/25/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
chooseCRANmirror(graphics=FALSE, ind=1)
library(formatR)
knitr::opts_chunk$set(tidy.opts = list(width.cutoff = 60), tidy = TRUE)
```

```{r set up workspace}
library(ggplot2)
library(tidyverse)
library(moderndive)
library(skimr)
library(infer)
library(dbplyr)
setwd("~/Desktop")
load(file="US_COVID19_21_10_29.RData")

```
##1

###a

```{r}
glimpse(us_counties)
us_counties %>% sample_n(5)
us_counties <- us_counties %>% mutate(cases_per_100000 = cases / pop_2019 * 100000)

```
There's one date(2021-10-19) of COVID data in this file.

### b

```{r}
county_sample <- us_counties %>% sample_n(50) %>% select(state, county, cases_per_100000)
glimpse(county_sample)
sample_n(county_sample, 5)
county_sample %>% skim_without_charts() 
mean(county_sample$cases_per_100000)
median(county_sample$cases_per_100000)
```
First run result:
Mean: 14604.66
Median: 14194.23
The data is right skewed.
This matches my intuition because the number of states which have more cases_per_100000 is smaller than the number of states which have less cases_per_100000 so that the mean is higher than the median.

### c 

```{r}
county_sample %>% ggplot(aes(x = cases_per_100000)) + geom_histogram(bins = 25 ) + labs(x="Cases_per_100000", y="Count", title="The rates of COVID cases per 100000")
```
Does the skew match your expectation based on the mean and median? Do the mean and median you computed above seem to match this histogram?

Yes. The skew matches my expectation because it has a longer right tail than left tail. it's right skewed and its mean is higher than the median. Yes, the mean and median result I computed matches the histogram.


### d

```{r}
county_resample <- county_sample %>% rep_sample_n(size = 50, reps = 1, replace = TRUE)
county_resample %>% group_by(state, county) %>% summarise(count = n()) %>% arrange(desc(count))
mean_resample <- county_resample %>% group_by(replicate) %>% summarize(mean = mean(cases_per_100000))
mean_resample
```


### e

```{r}

county_resample2 <- county_sample %>% 
  rep_sample_n(size = 50, replace = TRUE, reps = 35)

resample_mean <- county_resample2 %>% 
  group_by(replicate) %>% 
  summarize(mean_prop = mean(cases_per_100000))

ggplot(resample_mean, aes(x = mean_prop)) +
  geom_histogram(binwidth = 100, color = "white") +
  labs(x = "Mean Cases", y = "Count", title = "The rates of COVID cases per 10000 with Replicate 35")
resample_mean

```

### f

```{r}
county_resample3 <- county_sample %>% 
  rep_sample_n(size = 50, replace = TRUE, reps = 1000)

resample_mean <- county_resample3 %>% 
  group_by(replicate) %>% 
  summarize(mean_prop = mean(cases_per_100000))

ggplot(resample_mean, aes(x = mean_prop)) +
  geom_histogram(binwidth = 100, color = "white") +
  labs(x = "Mean Cases", y = "Count", title = "The rates of COVID cases per 10000 with Replicate 1000")
resample_mean
```
This histogram seems to have similar shape when compares with the previous one but it's much more accurate.
A larger number of resamples in a bootstrap leads to a smaller standard error so that the estimation of the population is more accurate.

### g

```{r}
bootstrap_distribution <- county_sample %>% specify(response = cases_per_100000) %>% generate(reps = 1000, type = "bootstrap") %>% calculate(stat = "mean")
visualize(bootstrap_distribution)
```
The bootstrap distribution specify() the variables of interest and generate() many replicates of bootstrap resampling with replacement, the calculate() function summarize each of the 1000 resamples of size 50 to a single sample statistic value. Then, visualize() provides a way to visualize the bootstrap distribution as a histogram. 

In this case, this bootstrap distribution has a longer right tail so it is an right skewed distribution as the previous ones.

### h
A bootstrap percentile CI of an estimator of theta is obtained by setting the lower and upper endpoints. The default is to calculate 95% confidence interval and in this case, the percentile method sets the lower endpoint at 2.5th percentile of the bootstrap distribution and the upper endpoint at the 97.5th percentile.


### i

```{r}
percentile_ci <- bootstrap_distribution %>% get_confidence_interval(level = 0.95, type = "percentile")
percentile_ci

visualize(bootstrap_distribution) + shade_confidence_interval(endpoints = percentile_ci )+ labs(x = "Stat", y = "Count", title = "Mean County Cases per 100000 between the northeast and the west")
```
The 95% confidence interval: (13694.83,15606.63)

### j
In order to use the standard error method,the bootstrap distribution must be a normal distribution.
The standard error method sets the endpoints argument to be standard_error_ci.
When the CI is 95%, the standard error is the sum of sample mean and the difference within 1.96 standard deviations of the mean.

### k
```{r}
standard_error_ci <- bootstrap_distribution %>% get_confidence_interval(type = "se", point_estimate = 14604.66)
standard_error_ci

visualize(bootstrap_distribution) + shade_confidence_interval(endpoints = standard_error_ci)
```
The 95% confidence interval: (13641.92,15567.4)

### l
```{r}
us_counties <- us_counties %>% mutate(cases_per_100000 = cases / pop_2019 * 100000)
mean(us_counties$cases_per_100000)
```
Yes, they seem vary similar. The true mean cases per 100000 from the us counties tibble is 14533.49 and it's in both intervals, so the intervals ‘catch’ the truth.


##2
We say that if a numerical variable follows a normal distribution, or, in other words, the histogram of this variable is bell-shaped, then roughly 95% of values fall between
± 1.96 standard deviations of the mean.